---
title: "Project2"
author: "Mohamed Elashri"
date: "March 22, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Statistical Inference Course Project 2


## Introduction 
Load the ToothGrowth data and perform some basic exploratory data analyses


## Load the ToothGrowth data and perform some basic exploratory data analyses

```{r}
#  libraries
library(ggplot2)
library(datasets)
library(gridExtra)
library(GGally)

# The Effect of Vitamin C on Tooth Growth in Guinea Pigs
data(ToothGrowth)
toothGrowth <- ToothGrowth 
toothGrowth$dose <- as.factor(toothGrowth$dose) #  factor conversion 

```

## basic summary of the data

```{r}
str(toothGrowth)

```

```{r}
summary(toothGrowth)

```

```{r}
head(toothGrowth)

```

```{r}
table(toothGrowth$supp, toothGrowth$dose)

```

Now we do Analysis of Variance ANOVA test 

```{r}
anova <- aov(len ~ supp * dose, data=toothGrowth)
summary(anova)

```


Results here support that there is a notable interaction between the length (len) and dosage (dose) with F values is 15.572 and with p<0.01. Also there is weak interaction between the combination of supplement type (supp) and dosage (dose) compared to the length (len) , F= 4.107 , p<0.05. 

## Use confidence intervals

```{r}
confint(anova)

```

```{r}
print(model.tables(anova,"means"),digits=3)

```

## conclusions 

from our observation, We  conclude that a higher dose is the main factor to increase the Tooth Growth using VC but OJ has better results at lower doses. 