---
title: "project1"
author: "Mohamed Elashri"
date: "March 22, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Statistical Inference Course Project


In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

## Simulation 

```{r}
library(ggplot2)
set.seed(11081979)

lamda <- 0.2
n <- 40 # exponetials number 
NS <- 1000 # tests number

          exp_sim <- function(n, lamda)
            {
                      mean(rexp(n,lamda))
            }
            
            sim <- data.frame(ncol=2,nrow=1000)
            names(sim) <- c("Index","Mean")

            for (i in 1:NS)
            {
                      sim[i,1] <- i
                      sim[i,2] <- exp_sim(n,lamda)
            }

 
```

## Sample Mean vs Theoretical Mean

### Sample Mean
```{r}
sample_mean <- mean(sim$Mean)
 
sample_mean
```

### Theoretical Mean

```{r}
mean_theory <- 1/lamda
mean_theory

```


## Histogram 
```{r}
hist(sim$Mean, 
  breaks = 100, 
   prob = TRUE, 
    main="Exponential Distribution for n = 1000", 
    xlab="Spread of values")
         abline(v = mean_theory, 
             col= 3,
              lwd = 2)
                 abline(v = sample_mean, 
                    col = 2,
                      lwd = 2)

legend('topright', c("Sample Mean", "Theoretical Mean"), 
   bty = "n",       
    lty = c(1,1), 
     col = c(col = 3, col = 2))

```

## Sample Mean vs Theoretical Mean

The expected mean $??$ of a exponential distribution of rate $??$ is

$?? = \frac{1}{??}$

```{r}
sample_var <- var(sim$Mean)
theor_var <- ((1/lamda)^2)/40

```


so the theoretical variance of the population is 
```{r}
theor_var
```

and sample variance is
```{r}
sample_var
```

and this is Histogram of values
 
```{r}
          hist(sim$Mean, 
                        breaks = 100, 
                        prob = TRUE, 
                        main = "Exponential Distribution n = 1000", 
                        xlab = "Spread of values")
                        lines(density(sim$Mean))
                        abline(v = 1/lamda, col = 3)
                        xfit <- seq(min(sim$Mean), max(sim$Mean), length = 100)
                        yfit <- dnorm(xfit, mean = 1/lamda, sd = (1/lamda/sqrt(40)))
                        lines(xfit, yfit, pch = 22, col = 4, lty = 2)
                        legend('topright', c("Simulated Values", "Theoretical Values"), 
                        bty = "n", lty = c(1,2), col = c(4, 3))

```
As we can see the standard deviations are very close Since variance is the square of the standard deviations.

## Distribution

we can see that this distribution is nearly linear as follows 

```{r}
qqnorm(sim$Mean, 
        main ="Normal Plot")
        qqline(sim$Mean, 
        col = "3")

```



